Manuscript

### 2018-01-05 manuscript.Rmd
Add discussion of log-sum calculation

# Results

## Denver

Plot Denver geospatial data (tracts and parks):
```{r denver_data}

#denver_tracts2 <- readOGR(dsn = "data/Denver_Data.gdb", layer = "Denver_Final") 
plot(boston_tracts)
#plot(denver_tracts)
#plot(nyc_tracts)

#denver_parks2 <- readOGR(dsn = "data/Denver_Data.gdb", layer = "Denver_All_Parks") 
plot(boston_parks)
#plot(denver_parks)
#plot(nyc_parks)
```

Transform the attribute table into a tibble and select the relevant variables:
```{r transformdata}
#TODO: make sure all cities have the same data in the same names. It will save 
# us LOTS of time
# denver only, because the other cities have different variables
regression_data <-
  lapply(seq_along(1:length(cities)), function(i) {
    tbl_df(tract_shapes[[i]]@data) %>%
      mutate(
        Park_Percent = ifelse(is.na(Park_Percent), 0, Park_Percent),
        city = cities[i]
      )
  })
```

```{r}
boston_plots <- spTransform(boston_tracts, CRSobj = CRS("+init=epsg:4326"))
denver_plots <- spTransform(denver_tracts, CRSobj = CRS("+init=epsg:4326"))
nyc_plots <- spTransform(nyc_tracts, CRSobj = CRS("+init=epsg:4326"))
library(leaflet)
leaflet() %>%
  addTiles() %>%
  #addPolygons(data = nyc_plots)
  #addPolygons(data = denver_plots)
  addPolygons(data = boston_plots)
```

DISCUSSION OF LOGSUM CALCULATION

Calculate the logsum given the tracts and parks dataset:
```{r accessibility}
betas <- list(
  boston = c(0.00001, -30), 
  denver = c(0.00001, -15), 
  nyc = c(0.0001, -5)
)
for(i in 1:length(cities)){
  regression_data[[i]]["park_ls"] <- calculate_park_logsums(
    tract_shapes[[i]], park_shapes[[i]], betas = betas[[i]])
}
```

Create regression equations for use in spatial econometric models:

We looked at income and it doesn't matter.
```{r regression_eq}
base_formula <- formula(
  ~ log(Pop_Density) + FulltimeWork + 
    CollegeDeg + SinglePercent + Pct0to17 + Pct18to29 + Pct30to64 + 
    Pct65plus + PctWhite + PctBlack + PctNative + PctAsian + PctPacific + 
    PctOther + PctHispanic)

>>>>

Consider that an individual is choosing a park for a recreation activity.
According to basic choice theory (Mcfadden 1974), the probability of choosing
park $i$ from the set of all regional parks $P$ is:

$$ P(i | V_i) = \frac{\exp(V_i)}{\sum_{j \in P}\exp(V_j)}$$
where parks are differentiated from each other by their relative measurable
utilitie $V$. In principle, $V$ may include any measurable attributes of either
the choice maker or the park. In this study we use an elementary linear formulation of

$$V_i = \beta_a acreage + \beta_d distance$$
incorporating the size of the park in acres and the distance of the park from
each census tract in miles. The coefficients $\beta$ are typically estimated from 
surveys, though in the absence of a survey we apply a maximum likelihood
technique described below.

A key theoretical understanding of random utility choice models is that the
consumer surplus of the choice set can be otained as the log-sum of the
denominator of the choice probability equation. In plainer terms, the *total value*
of an individual's park accessibility is defined to be:

$$\ln\left({\sum_{j \in P}\exp(V_j)}\right)$$

There are several advantages to a log-sum defined metric relative to
buffer-based accessibility metrics more commonly found in the literature. First,
all individuals are defined as having some access to all parks, rather than an
arbitrary limit of 1/2 mile or so. This allows for the fact that some people are
more or less sensitive to distances, and that distance is a continuous, and not
a binary, phenomenon. Second, the random utility formulation allows the
researcher to include any attribute of the park; in this case, we consider the
size of the park as an element of accessibility. This suggests that not all
parks are equal, and that a large park such as New York City's Central Park may
provide health and activity benefits over a much larger area than a smaller
community square.

McFadden, D. (1974). The measurement of urban travel demand. Journal of public economics, 3(4), 303-328.

In the absence of a park choice survey, we estimated likely values of the $\beta$ 
coefficients by iteratively searching for the values which produced the highest
model likelihood in *which model did we use to estimate likelihood?*. The search
was constrained by two assertions. First, we required that the coefficient on
size be positive and that on distance negative; all else equal, people will
prefer to use larger parks that are nearer to their residence. Second, we visually
inspected the resulting accessibility scores to ensure that the scores produced a 
reasonably varied pattern of access throughout the metropolitan region.

```{r transformdata}
#TODO: make sure all cities have the same data in the same names. It will save 
# us LOTS of time
# denver only, because the other cities have different variables
regression_data <-
  lapply(seq_along(1:length(cities)), function(i) {
    tbl_df(tract_shapes[[i]]@data) %>%
      mutate(
        Park_Percent = ifelse(is.na(Park_Percent), 0, Park_Percent),
        city = cities[i]
      )
  })
```

```{r city_plots, eval = FALSE}
boston_plots <- spTransform(boston_tracts, CRSobj = CRS("+init=epsg:4326"))
denver_plots <- spTransform(denver_tracts, CRSobj = CRS("+init=epsg:4326"))
nyc_plots <- spTransform(nyc_tracts, CRSobj = CRS("+init=epsg:4326"))
library(leaflet)
leaflet() %>%
  addTiles() %>%
  #addPolygons(data = nyc_plots)
  #addPolygons(data = denver_plots)
  addPolygons(data = boston_plots)
```

```{r betas}
betas <- list(
  boston = c(0.00001, -30), 
  denver = c(0.00001, -15), 
  nyc = c(0.0001, -5)
)
```

Calculate the logsum given the tracts and parks dataset:
```{r accessibility}
for(i in 1:length(cities)){
  regression_data[[i]]["park_ls"] <- calculate_park_logsums(
    tract_shapes[[i]], park_shapes[[i]], betas = betas[[i]])
}
```

# Results
Create regression equations for use in spatial econometric models:
We looked at income and it doesn't matter.
```{r regression_eq}
base_formula <- formula(
  ~ log(Pop_Density) + FulltimeWork + 
    CollegeDeg + SinglePercent + Pct0to17 + Pct18to29 + Pct30to64 + 
    Pct65plus + PctWhite + PctBlack + PctNative + PctAsian + PctPacific + 
    PctOther + PctHispanic)
